---
title: "Wine Review Analysis and Data Visualization"
author: "Ziwei Wang (RUID:181002134)"
output: html_document
font size: 11pt
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(readxl)
library(tidyverse)
library(broom)
library(tidyr)
library(tidytext)
library(wordcloud)
library(dplyr)
```

## 1 Introduction
Wine is an alcoholic drink popular with the whole world. It can be used at various occasions. A glass of wine before bed will help people get a better night. According to new research, It can even help people to live longer. Different varieties of grapes produce different types of wine, which has different flavor. This may result in difficulties for beginners to choose wine.  

In this report, we access to a database on kaggle which consists of thousands of wine reviews, ratings and prices. Our goal is to explore wines from around the world and give some advice to beginners on wine selection. We also compare these data to the world wine consumption and production data to find relationships between them. The consumption and production statistics are from Organization Internationale de la vigne et du vin(OIV) 2013-2014 report.


## 2 Data Processing
In this section, we describe some preprocessing steps that we performed preliminary to the analysis of
the data. We have three original datasets. The first one is the wine review dataset, consisting of approximately 13000 entries, with 10 variables including country, description, designation, points, price, province, region, tester name, variety, winery and so on. After removing missing values, we select 5 variables: country, description, points(wine score), price and variety(grape variety) with 120916 observations in total. The second and third datasets are world wine consumption and production in 1000hectolitres(1000HI) by country respectively. We select statistics in year 2013 and 2014 because these two years match the production year of wines in the wine review data set. For world wine consumption data, 77 countries are included while for world wine production data, 63 countries are included. Below are the parts of the three datasets.

```{r,echo=FALSE}
wine_review = read.csv("wine_review_data.csv") %>% 
  select(country, description, points, price, variety) %>% filter(!is.na(price)) %>% filter(country != "")
knitr::kable(
  head(wine_review, n = 3), 
  caption = "Table1: Wine Review Data"
)
```

```{r}
wine_consumption = read_xlsx("world wine consumption.xlsx",skip = 3) %>% 
  rename(country = X__1, Y2013 = X__7, Y2014 = X__8) %>% filter(!is.na(Y2013)) %>% 
  filter(!is.na(Y2014)) %>% select(country, Y2013, Y2014) %>% 
  filter(!country %in% c("Other African Countries","Total Africa", "Other American Countries", "Total America","Other Asian Countries", "Total Asia", "Total Europe", "Other Oceanian Countries", "Total Oceania", "World Total", "2009"))
wine_consumption$Year2013 = gsub(" ", "", wine_consumption$Y2013, fixed = TRUE)
wine_consumption$Year2014 = gsub(" ", "", wine_consumption$Y2014, fixed = TRUE)
wine_consumption = wine_consumption %>% select(country, Year2013, Year2014)
knitr::kable(
  head(wine_consumption, n = 3), 
  caption = "Table2: Wine Consumption Data"
)
```

```{r}
wine_production = read_xlsx("world wine production.xlsx",skip = 3) %>% 
  rename(country = X__1, Y2013 = X__7, Y2014 = X__8) %>% filter(!is.na(Y2013)) %>% 
  filter(!is.na(Y2014)) %>% select(country, Y2013, Y2014) %>% 
  filter(!country %in% c("Other African Countries","Total Africa", "Other American Countries", "Total America","Other Asian Countries", "Total Asia", "Total Europe", "Other Oceanian Countries", "Total Oceania", "World Total", "2009"))
wine_production$Year2013 = gsub(" ", "", wine_production$Y2013, fixed = TRUE)
wine_production$Year2014 = gsub(" ", "", wine_production$Y2014, fixed = TRUE)
wine_production = wine_production %>% select(country, Year2013, Year2014)
knitr::kable(
  head(wine_production, n = 3), 
  caption = "Table 3: Wine Production Data"
)
```


## 3 Best wine producing countries
First, we look at the average score of wine in each country. Wine in England scores the best with point 91.55. Wine in Peru had the least avergae point, which is 83.56. The score of India and Austria are very similar, 90.22 and 90.19 respectively. The next four countries that won good scores that nearly 90 are Germany, Canada, Hungary and China. The rest three countries in the top three lists are France, Lusembourg and Italy, scores all round 88. However, the average point does not completely represent the quality. We should also look at wine in specific range.

```{r}
average_point = wine_review %>%
    group_by(country)%>%
    summarize(avg_point = mean(points))%>% 
    arrange(desc(avg_point)) 
#knitr::kable(
  #head(average_point, n =10), 
  #caption = "Table 4: Wine Average Score by Country"
#)
```

We define a wine to be the best as it has score over 95. There are total 2211 wines scoring over 95 and 14 countries have these qualifies wines. From the plot, we can see that the top five best wine producing countries are US, France, Italy, Austria and Portugal. Among them, the number of wine which scores greater than 95 in US takes approximately 50 percent. It is alomost twice more than the number in France, which ranks second.

```{r, echo=FALSE}
best_wine_country = wine_review %>% filter(points >= 95) %>% group_by(country) %>% summarise(n = n()) %>% arrange(desc(n))
top_five = head(best_wine_country, n = 5) %>%
  ggplot(aes(x= reorder(country,-n), y = n)) +  
  geom_bar(stat="identity", fill = c("#60282e", "#722f37", "#843640", "#963e48", "#a84551") ) + 
  xlab("country")+ ggtitle("Best Wine Producing Countries") + 
  theme(
plot.title = element_text(color="#3c191d", size=14, face="bold"),
axis.title.x = element_text(color="#3c191d"),
axis.title.y = element_text(color="#3c191d")
)
top_five
```


## 4 Grape Variety of Wine by Country
We check only the top three best wine producing countries, US, France and Italy, to see what kind of the grape they like to use.

```{r,echo=FALSE}
grape_variety = wine_review %>% select(country,variety)
variety_by_country = function(string, adjusted = FALSE){
  grape_variety %>% filter(country == string) %>% 
    group_by(variety) %>% 
    summarise(n= n()) %>% 
    arrange(desc(n)) %>% 
    head()
}

knitr::kable(
  variety_by_country("US"), 
  caption = "Table 4: Grape Variety of Wine in US"
)

knitr::kable(
  variety_by_country("Italy"), 
  caption = "Table 5: Grape Variety of Wine in Italy"
)

knitr::kable(
  variety_by_country("France"), 
  caption = "Table 6: Grape Variety of Wine in France"
)
```

US wines are more likely to use Pinot Noir, Cabernet Sauvignon, Chardonnay, Syrah, Red Blend and Zinfandel. Italy wines prefer Red Blend, Nebbiolo, Sangiovese, White Blend, Glera and Sangiovese Grosso. Wine in France Bordeaux-style Red Blend, Chardonnay, RosÃ, Pinot Noir, Champagne Blend and Gamay. We can find that Pinot Noir, Chardonnay and Red Blend are three grape varieties chosen by at least two countries.


## 5 Best Wine Producing Grape Varieties
The top ten best wine producing grape varieties are Pinot Noir, Cabernet Sauvignon, Chardonnay, Riesling, Bordeaux-style Red Blend, Nebbiolo, Red Blend, Syrah, Sangiovese and Champagne Blend. They are all popular grape varities used by top five wine producing countries except Riesling, which is commonly used by German. Below is the top five best wine producing grape varieties plot.

```{r, echo=FALSE}
best_wine_variety = wine_review %>% filter(points >= 95) %>% group_by(variety) %>% summarise(n = n()) %>% arrange(desc(n))
top_ten = head(best_wine_variety, n = 5) %>%
  ggplot(aes(x= reorder(variety,-n), y = n)) +  
  geom_bar(stat="identity", fill = c("#60282e", "#722f37", "#843640", "#963e48", "#a84551") ) + 
  xlab("variety")+ ggtitle("Best Wine Producing Grape Varieties") + 
  theme(
plot.title = element_text(color="#3c191d", size=14, face="bold"),
axis.title.x = element_text(color="#3c191d"),
axis.title.y = element_text(color="#3c191d")
)
top_ten
Riesling = wine_review %>% filter(variety == "Riesling") %>% group_by(country) %>% summarise(n = n()) %>% arrange(desc(n)) %>% head(n =3)
```

Pinot Noir is the world’s most popular light-bodied red wine, with primary flavor of cherry, raspberry, mushroom, vanilla and hibiscus. It is always dry and has spice aroma, accentuated by a long, smooth finish. It pairs particularly well with duck, chicken, pork, and mushrooms.

Cabernet Sauvignon is loved for its high concentration and age worthiness. The primary flavor of wine made of this grape variety is consisted of cherry, black currabt, cedar, baking Speices and Graphite.The rich flavor and high tannin content in Cabernet Sauvignon make it a perfect partner to dishes with high flavor.

Chardonnay has primary flavors of yellow apple, starfruit, pineapple, vanilla and butter. It will keep spice and flavor intensity low while accentuating creamy, buttery flavors and textures. This is a wine worthy of lobster.

Riesling is an aromatic white variety that flavors like lime, green apple, beeswax, jasmine and petrol. Off-dry Riesling wines make a great pairing to spicy Indian and Asian cuisines and do excellently alongside duck, pork, bacon, shrimp and crab.

Bordeaux-style Red Blends are known for their powerful structure and deep flavors. Dark fruits and berries such as plum and blackcurrant are commonly used to describe the flavors of red Bordeaux. Food matches for Bordeaux Blend wines include: steak, rib-eye fillet and oast leg of lamb with rosemary and garlic.


## 6 Price
### 6.1 Wine Price
For all the reviewed wines, the Lowest price is $4. 5 are from US, Five are from Spain, the rest two are from Argentina and Romania respectively. While, the highest price is $3300, from France, with grape variety Bordeaux-style Red Blend. After calculating the average wine price of each country, Switzerland ranks the first with 85.29 dollars. Following are England(51.68), Germany(42.26), France(41.14) and Hungary(40.65).

```{r,echo=FALSE}
wine_price = wine_review %>% select(country, price, variety)
highest = wine_price %>% filter(price == "3300")
lowest = wine_price %>% filter(price == "4") %>% group_by(country) %>% count()

average_price = wine_price %>%
    group_by(country)%>%
    summarize(avg_price = mean(price))%>% 
    arrange(desc(avg_price)) 

#knitr::kable(
  #average_price, 
  #caption = "Table 7: Wine Average Price by Country"
#)
```


We check 100 most expensive and cheapest wines. The results show that France produces most number of costly wines. The other four countries that produces costly wines are Italy, Germany, Portugal and US. However, US also produces most number of ecnomic wines, followed by Portugal, Spain, Italy and Argentina.

```{r,echo=FALSE}
costly_wine = wine_price %>% arrange(desc(price)) %>% head(n = 100) %>% group_by(country) %>% count() %>% arrange(desc(n)) %>% head(n = 5)
knitr::kable(
  costly_wine, 
  caption = "Table 7: Costly Wine"
)
```

```{r}
economic_wine = wine_price %>% arrange((price)) %>% head(n = 100) %>% group_by(country) %>% count() %>% arrange(desc(n)) %>% head(n = 5)
knitr::kable(
  economic_wine, 
  caption = "Table 8: Economic Wine"
)
```


### 6.2 Variety Price
For all the 692 grape varieties, Trajadura is the cheapest while Ramisco is the most expensive grape vaiety, with average price reaches up to $495. The top five varieties with high average price are Ramisco, Terrantez, Francisa, Rosenmuskateller and Malbec-Cabernet. It is worth mentioning that none of those varieties show in the list of best wine producing varieties.  

We also check 100 most expensive and cheapest varieties. The results show that Chardonnay, Bordeaux-style Red Blend, Pinot Noir, Bordeaux-style white Blend and Riesling are the most costly variesties. It is intersting that Chardonnay also appears in the most economic variety list and rank the first. The other four less expensive varieties are Cabernet Sauvignon, Portuguese Red, Tempranillo and white blend.

```{r,echo=FALSE}
average_variety_price = wine_price %>%
    group_by(variety)%>%
    summarize(avg_price = mean(price))%>% 
    arrange(desc(avg_price))

costly_variety = wine_price %>% arrange(desc(price)) %>% head(n = 100) %>% group_by(variety) %>% count() %>% arrange(desc(n)) %>% head(n = 5)
knitr::kable(
  costly_wine, 
  caption = "Table 9: Costly Variety"
)
```

```{r}
economic_variety = wine_price %>% arrange((price)) %>% head(n = 100) %>% group_by(variety) %>% count() %>% arrange(desc(n)) %>% head(n = 5)
knitr::kable(
  economic_variety, 
  caption = "Table 10: Economic Variety"
)
```


## 7 Compare with the world wine production and consumption by country table
We calculate the average of consumption and production of wine by using the mean value of statistics in year 2013 and 2014.
```{r}
consumption = wine_consumption %>% 
  mutate(consume_avg = (as.integer(Year2013) + as.integer(Year2014))/2)
consumption$country = as.character(gsub("USA", "US", consumption$country))
consumption$country = as.character(gsub("United Kingdom", "England", consumption$country))

production = wine_production %>% mutate(produce_avg = (as.integer(Year2013) + as.integer(Year2014))/2)
production$country = as.character(gsub("USA", "US", production$country))
production$country = as.character(gsub("United Kingdom", "England", production$country))

comparison = wine_review %>% group_by(country) %>% summarise(n = n()) %>% 
  left_join(consumption, by = "country") %>% 
  left_join(production, by = "country") %>% 
  arrange(desc(n)) %>% 
  mutate(consume_rank = dense_rank(desc(consume_avg))) %>% 
  mutate(produce_rank = dense_rank(desc(produce_avg))) %>%
  select(country, n, consume_avg, consume_rank, produce_avg, produce_rank)

knitr::kable(
  head(comparison, n = 10), 
  caption = "Table 10: Consumption and  Production Comparison"
)
```

The table shows that US has most number of wines been reviewed, which matches its rank in consumption list. However, it ranks 4th in the production list. French people contribute the same to both wine consumption and production industy. Their wines were reviewed the second place. According to the table, Italy produces most amount of wine while its citizens consume not a few, with 20.1MHIs. It looks like that Spanish are more likely to produce wine that Spain is the third largest wine production country, nearly five times as its consumption. The same thing happens to Chile. More interestingly, Germany is opposite to Spain. It is the third largest wine consumption country which their production ranks only 10th. The consumption is twice more than the production. German might be happier if they can produce larger amount of wine themselves.


## 8 Wine Word Cloud By Country and variety
We choose the countries that have great consumption and production, also are on the list of best wine producing countries, with their representative and high quality variety to make four wordclouds. In addition of removing the stop words in the description, we also remove the non-descriptive word that is possible to appear in the wine review, like grape, aroma(s), ripe and tastes, to make the result more precise and targeted.

```{r,echo=FALSE}
wine_description = wine_review %>% select(country, variety) %>% 
  mutate(description = str_extract(as.character(wine_review$description), "[a-zA-Z]+"))
wine_word = data.frame(word = c("grape","aroma", "aromas","ripe","tastes"))
wordcloud_by_country_variety = function(c, v){
  wine_description %>% filter(country == c) %>% filter(variety == v)%>% unnest_tokens(word, description) %>% 
  anti_join(stop_words, by = "word") %>% anti_join(wine_word, by = "word") %>%
  count(word) %>% arrange(desc(n)) %>% with(wordcloud(word, n, max.words = 20,
            colors=brewer.pal(9, "Reds"),
            random.color=TRUE,random.order=FALSE))
}

```

###8.1 US- Pinot Noir Wordcloud
```{r}
wordcloud_by_country_variety("US", "Pinot Noir")
```

The most common words used to describe US- Pinot Noir are light, juicy, dry, rich, bright, spicy, tight and so on.

###8.2 France- Bordeaux-style Red Blend Wordcloud
```{r}
wordcloud_by_country_variety("France", "Bordeaux-style Red Blend")
```

The most common words used to describe France- Bordeaux-style Red Blend are produced, rich, firm, soft, wood, fresh, solid, smoky, structured and so on.

###8.3 Italy- Red Blend Wordcloud
```{r}
wordcloud_by_country_variety("Italy", "Red Blend")
```

The most common words used to describe Italy- Red Blend are underbrush, bright, alluring, vibrant, subtle, fragrant, wild and so on.

###8.4 Germany- Riseling Wordcloud
```{r}
wordcloud_by_country_variety("Germany", "Riesling")
```

The most common words used to describe Germany- Riseling are whiffs, rich, fresh, savory, sweet, smoke, intensely, pristine, intense, dusty, delicate and so on.

## 9 Conclusion
In conclusion, US, France and Italy are three main countries that contributes a lot to wine industry. Pinot Noir, Cabernet Sauvignon and Bordeaux Blend are commonly seen grape varieties that seldom goes wrong. High wine price does not necessarily mean nice wine taste. Sometimes, spending thousand dollors may just get back nothing. For beginners, the wine from those three countires with the popular grape varieties are good choices.  For people who have more requirement on the taste and food pair, Pinot Noir is smoothy and spicy, suitable with poultry and pork. Cabernet Sauvignon has rich flavor and high tannins and it is better serve with high flavor dishes. Bordeaux Blends has powerful structure and deep flavor and has food-pair with steak and lamb. 

In the future study, we will focus on finding the factors that might influence wine's price and score. We will build models like linear regression model or logistic regression model to find the relationship between price and other variables.


























